Scheduling and Amortization for MPC

### 2022-01-06 paper_SIMD.tex
updated assumption comments

\begin{enumerate}
\item All statements in the program execute using the same protocol (sharing). That is, there is no share conversion. \ishaq{We should say somewhere (in a footnote?) that we know this is not ideal, otherwise reviewers will complain.}
\item All MPC instructions have the same unit cost, 1 unit. \ishaq{Don't we need to distinguish between local (cheap) vs. interactive (expensive) instructions? I don't see how we could assume this. -- Past suggestion from Vassilis: Ideally we should assume cost to be a convex function.}
\item There is unlimited bandwidth---i.e., a single MPC-instruction costs as much as $N$ amortized instructions, namely 1 unit.\ishaq{This is fair for theoretical model, although in some real life applications this is not true, e.g. L2 norm of large vectors.}
\item MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
2 MUL instructions scheduled in parallel benefit from amortization and cost 1, however a MUL and a MUX instructions scheduled
in parallel still cost 2. \ishaq{This is not true, can we still assume it? -- YES.}
\end{enumerate}

>>>>

\begin{enumerate}
\item All statements in the program execute using the same protocol (sharing). That is, there is no share conversion. \ishaq{This is not an assumption, this is our setting. We work in the single protocol world.}
\item All MPC instructions have the same unit cost, 1 unit. \ishaq{Don't we need to distinguish between local (cheap) vs. interactive (expensive) instructions? I don't see how we could assume this. -- Past suggestion from Vassilis: Ideally we should assume cost to be a convex function.}
\item There is unlimited bandwidth---i.e., a single MPC-instruction costs as much as $N$ amortized instructions, namely 1 unit.\ishaq{Comment from Vassilis: We assume there are infinite parallel capacities, this is the standard assumption in PRAM (Cryptographic Parallel RAM).}
\item MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
2 MUL instructions scheduled in parallel benefit from amortization and cost 1, however a MUL and a MUX instructions scheduled
in parallel still cost 2. \ishaq{We need to reword this assumption to something like "$K$ parallel MUL costs much less than $K$ (because they get amortized), but any mix of $K$  MUL and MUX still cost roughly $K$. Specifically, we should take away the low constants (2 and 1) because we know for low constants this is not true.}
\end{enumerate}
